### 2024-11-30 site/index.qmd
pushing v0

---
title: "Nic Steyn"
image: files/index/me.jpg
page-layout: full

about:
  id: about
  template: trestles
  image-width: 70%
  links:
    - icon: github
      text: Github
      href: https://github.com/nicsteyn2
    - text: "{{< ai google-scholar >}} Google Scholar"
      href: https://scholar.google.com/citations?user=DyNrh4cAAAAJ
      target: _blank
    - icon: envelope
      text: Email
      href: mailto:nic.steyn@outlook.com
    - icon: linkedin
      text: LinkedIn
      href: https://www.linkedin.com/in/nic-steyn/
      target: _blank
    - text: "{{< ai orcid >}} ORCID"   # use academic icons, "" are needed
      href: https://orcid.org/0000-0001-8904-2941
      target: _blank
    # - icon: globe
    #   text: Department of Statistics
    #   href: https://www.stats.ox.ac.uk/people/nicholas-steyn
    #   target: _blank

# listing:
#   - id: recent-posts
#     contents: 
#       - posts
#       - posts/post-links.yml
#     exclude:
#       title: "Participating APPAM 2024"
#     type: grid
#     max-items: 3
# #    image-height: 150px
#     page-size: 3 #set same as max-times to remove the page number setting
#     fields: [image, date, title, author, description]
#     max-description-length: 75
#     sort: 
#       - "date desc"
#       - "title asc"
---

:::{#about}

## Bio

I am a doctoral student on the [Modern Statistics and Statistical Machine Learning CDT](https://statml.io) at the University of Oxford, supervised by Professor Christl Donnelly and Dr Kris V Parag.

My thesis focusses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators). My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as survey data and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).

During my studies, I have also worked as a research assistant in the [*The Global Reference Group for Children Affected by Crisis*](https://www.spi.ox.ac.uk/the-global-reference-group-on-children-affected-by-covid-19#collapse3701021), estimating orphanhood in Brazil during the COVID-19 pandemic (publication coming soon), and have held a variety of tutoring positions (departmental, college, and inter-departmental courses).

Past experience includes modelling for policymakers during the COVID-19 pandemic in my home country of New Zealand (March 2020 - September 2021), a quantitative trading internship at Optiver in Sydney (November 2019 - January 2020), and a data analysis internship at a startup in Bangkok (January - February 2018).

## Education

**University of Oxford** | Oxford, United Kingdom<br>
DPhil in Statistics | 2021 - 2025

**University of Canterbury** | Christchurch, New Zealand<br>
BSc (Hons) Compuational and Applied Mathematics | 2019<br>
Awarded with first class

**University of Canterbury** | Christchurch, New Zealand<br>
BSc Financial Engineering and Statistics | 2016 - 2018<br>
GPA: 8.96 out of 9

I also studied statistics at **National University of Singapore** on an exchange programme in 2018.

:::

### 2024-11-30 site/papers.qmd
pushing v0

---
title: ""
toc: true
lightbox: true
---

# Pre-prints

**Steyn, N.**, & Parag, K. V. Robust uncertainty quantification in popular estimators of the instantaneous reproduction number. *medRxiv preprint*. [https://doi.org/10.1101/2024.10.22.24315918](https://doi.org/10.1101/2024.10.22.24315918)

**Steyn, N.**,  Parag, K. V., & Donnelly, C. A. A primer on inference and prediction with epidemic renewal models using sequential Monte Carlo methods. [Link to PDF](https://github.com/nicsteyn2/SMCforRt/blob/main/workingpaper.pdf)

# Online resources

[SMC and epidemic renewal models](https://nicsteyn2.github.io/SMCforRt/): an online "book" demonstrating sequential Monte Carlo methods for fitting epidemic renewal models. Accompanies *A primer on inference and prediction with epidemic renewal models using sequential Monte Carlo methods*.

[Rt estimators in Julia](https://nicsteyn2.github.io/RobustRtEstimators/): short vignettes accompanying the code provided in the [GitHub repository](https://github.com/nicsteyn2/RobustRtEstimators) for *Robust uncertainty quantification in popular estimators of the instantaneous reproduction number*. Provides Julia implementation of EpiEstim and EpiFilter, as well as the corresponding parameter fitting methodology developed in the paper.

# Posters

<div style="max-width: 600px; margin: 1 auto;">

::: {layout-ncol=2}

![Presented at IDM 2024. Download [here](../files/posters/idm_poster_2024.pdf).](../files/posters/idm_poster_2024.png)

![Presented at EPIDEMICS 2023. Download [here](../files/posters/epidemics_poster_2023.pdf).](../files/posters/epidemics_poster_2023.png)

:::

</div>

# Publications

### 2024

Watson, L. M., Plank, M. J., Armstrong, B. A., Chapman, J. R., Hewitt, J., Morris, H., Orsi, A., Bunce, M., Donnelly, C. A., & **Steyn, N**. Jointly estimating epidemiological dynamics of Covid-19 from case and wastewater data in Aotearoa New Zealand. *Communications Medicine*. [https://doi.org/10.1038/s43856-024-00570-3](https://doi.org/10.1038/s43856-024-00570-3)

### 2023

Binny, R. N., Priest, P., French, N. P., Parry, M., Lustig, A., Hendy, S. C., Maclaren, O. J., Ridings, K. M., **Steyn, N.**, Vattiato, G., & Plank, M. J. Sensitivity of Reverse Transcription Polymerase Chain Reaction Tests for Severe Acute Respiratory Syndrome Coronavirus 2 Through Time. *The Journal of Infectious Diseases*. [https://doi.org/10.1093/infdis/jiac317](https://doi.org/10.1093/infdis/jiac317)

Elliott, P., Whitaker, M., Tang, D., Eales, O., **Steyn, N.**, Bodinier, B., Wang, H., Elliott, J., Atchison, C., Ashby, D., Barclay, W., Taylor, G., Darzi, A., Cooke, G. S., Ward, H., Donnelly, C. A., Riley, S., & Chadeau-Hyam, M. Design and Implementation of a National SARS-CoV-2 Monitoring Program in England: REACT-1 Study. *American Journal of Public Health*. [https://doi.org/10.2105/AJPH.2023.307230](https://doi.org/10.2105/AJPH.2023.307230)

### 2022

Elliott, P., Eales, O., **Steyn, N.**, Tang, D., Bodinier, B., Wang, H., Elliott, J., Whitaker, M., Atchison, C., Diggle, P. J., Page, A. J., Trotter, A. J., Ashby, D., Barclay, W., Taylor, G., Ward, H., Darzi, A., Cooke, G. S., Donnelly, C. A., & Chadeau-Hyam, M. Twin peaks: the Omicron SARS-CoV-2 BA. 1 and BA. 2 epidemics in England. *Science*. [https://doi.org/10.1126/science.abq4411](https://doi.org/10.1126/science.abq4411)

Plank, M. J., James, A., Lustig, A., **Steyn, N.**, Binny, R. N., & Hendy, S. C. Potential reduction in transmission of COVID-19 by digital contact tracing systems: a modelling study. *Mathematical Medicine and Biology*. [https://doi.org/10.1093/imammb/dqac002](https://doi.org/10.1093/imammb/dqac002)

**Steyn, N.**, Lustig, A., Hendy, S. C., Binny, R. N., & Plank, M. J. Effect of vaccination, border testing, and quarantine requirements on the risk of COVID-19 in New Zealand: A modelling study. *Infectious Disease Modelling*. [https://doi.org/10.1016/j.idm.2021.12.006](https://doi.org/10.1016/j.idm.2021.12.006)

**Steyn, N.**, Plank, M. J., Binny, R. N., Hendy, S. C., Lustig, A., & Ridings, K. A COVID-19 vaccination model for Aotearoa New Zealand. *Scientific Reports* [https://doi.org/10.1038/s41598-022-06707-5](https://doi.org/10.1038/s41598-022-06707-5)

### 2021

Hendy, S., **Steyn, N.**, James, A., Plank, M. J., Hannah, K., Binny, R. N., & Lustig, A. Mathematical modelling to inform New Zealand’s COVID-19 response. *Journal of the Royal Society of New Zealand*. [https://doi.org/10.1080/03036758.2021.1876111](https://doi.org/10.1080/03036758.2021.1876111)

James, A., Plank, M. J., Hendy, S., Binny, R., Lustig, A., **Steyn, N.**, Nesdale, A., & Verrall, A. Successful contact tracing systems for COVID-19 rely on effective quarantine and isolation. *PLoS One*. [https://doi.org/10.1371/journal.pone.0252499](https://doi.org/10.1371/journal.pone.0252499)

**Steyn, N.**, Binny, R. N., Hannah, K., Hendy, S., James, A., Lustig, A., Ridings, K., Plank, M. J., & Sporle, A. Māori and Pacific People in New Zealand have higher risk of hospitalisation for COVID-19. *New Zealand Medical Journal*. [Link to PDF](https://nzmj.org.nz/media/pages/journal/vol-134-no-1538/maori-and-pacific-people-in-new-zealand-have-a-higher-risk-of-hospitalisation-for-covid-19/55602a1fe7-1696476650/maori-and-pacific-people-in-new-zealand-have-a-higher-risk-of-hospitalisation-for-covid-19-open-access.pdf)

James, A., Plank, M. J., Binny, R. N., Lustig, A., Hannah, K., Hendy, S. C., & **Steyn, N.** A structured model for COVID-19 spread: modelling age and healthcare inequities. *Mathematical Medicine and Biology*. [https://doi.org/10.1093/imammb/dqab006](https://doi.org/10.1093/imammb/dqab006)

Binny, R. N., Baker, M. G., Hendy, S. C., James, A., Lustig, A., Plank, M. J., Ridings, K. M., & **Steyn, N.** Early intervention is the key to success in COVID-19 control. *Royal Society Open Science*. [https://doi.org/10.1098/rsos.210488](https://doi.org/10.1098/rsos.210488)

**Steyn, N.**, Plank, M. J., James, A., Binny, R. N., Hendy, S. C., & Lustig, A. Managing the risk of a COVID-19 outbreak from border arrivals. *Journal of the Royal Society Interface*. [https://doi.org/10.1098/rsif.2021.0063](https://doi.org/10.1098/rsif.2021.0063)

Plank, M., James, A., & **Steyn, N.** Comment: weekly COVID-19 testing with household quarantine and contact tracing is feasible and would probably end the epidemic[^1]. *Royal Society Open Science*. [https://doi.org/10.1098/rsos.201546](https://doi.org/10.1098/rsos.201546)

[^1]: This is a published comment piece on a paper arguing that household quarantine and contact tracing would have been sufficient to end the pandemic. We were arguing that it would **not** have been sufficient.

James, A., Plank, M. J., Hendy, S., Binny, R. N., Lustig, A., & **Steyn, N.** Model-free estimation of COVID-19 transmission dynamics from a complete outbreak. *PLOS ONE*. [https://doi.org/10.1371/journal.pone.0238800](https://doi.org/10.1371/journal.pone.0238800)

### 2020

**Steyn, N.**, Binny, R. N., Hannah, K., Hendy, S., James, A., Kukutai, T., Lustig, A., McLeod, M., Plank, M. J., Ridings, K., & Sporle, A. Estimated inequities in COVID-19 infection fatality rates by ethnicity for Aotearoa New Zealand. *New Zealand Medical Journal*. [Link to PDF](https://nzmj.org.nz/media/pages/journal/vol-133-no-1521/estimated-inequities-in-covid-19-infection-fatality-rates-by-ethnicity-for-aotearoa-new-zealand/9bb9847717-1696476126/estimated-inequities-in-covid-19-infection-fatality-rates-by-ethnicity-for-aotearoa-new-zealand-open-access.pdf)

# Technical reports

**Steyn, N.**, Plank, M. J., & Hendy, S. C. Modelling to support a future COVID-19 strategy for Aotearoa New Zealand. (2021). [Link to PDF](https://bpb-ap-se2.wpmucdn.com/blogs.auckland.ac.nz/dist/d/75/files/2017/01/modelling-to-support-a-future-covid-19-strategy-for-aotearoa-new-zealand.pdf)

**Steyn, N.**, Hendy, S., Plank, M., & Binny, R. Technical report: modelling the potential spread of COVID-19 during the August 2021 outbreak. (2021).  [Link to PDF](https://bpb-ap-se2.wpmucdn.com/blogs.auckland.ac.nz/dist/d/75/files/2017/01/technical-report-28-august.pdf)

James, A., Binny, R. N., Hendy, S. C., Lustig, A., **Steyn, N.**, & Plank, M. J. Economic comparison of the use of Alert Levels 3 and 4 in eliminating the Auckland August outbreak: a cost-effectiveness analysis 21 October 2020. (2020). [Link to PDF](https://bpb-ap-se2.wpmucdn.com/blogs.auckland.ac.nz/dist/d/75/files/2020/11/Economic-comparison-Auckland-August-outbreak_forTPMwebpage_21Oct.pdf)

Binny, R. N., Hendy, S. C., James, A., Lustig, A., Plank, M. J., & **Steyn, N.** Probability of elimination for COVID-19 in Aotearoa New Zealand. (2020). [https://doi.org/10.1101/2020.08.10.20172361](https://doi.org/10.1101/2020.08.10.20172361)

Binny, R. N., Lustig, A., Brower, A., Hendy, S. C., James, A., Parry, M., Plank, M. J., & **Steyn, N.** Effective reproduction number for COVID-19 in Aotearoa New Zealand. (2020). [https://doi.org/10.1101/2020.08.10.20172320](https://doi.org/10.1101/2020.08.10.20172320)

Binny, R. N., Hendy, S. C., James, A., Lustig, A., Plank, M. J., & **Steyn, N.** Effect of Alert Level 4 on Reff: review of international COVID-19 cases. (2020). [https://doi.org/10.1101/2020.04.30.20086934](https://doi.org/10.1101/2020.04.30.20086934)

Plank, M. J., Binny, R. N., Hendy, S. C., Lustig, A., James, A., & **Steyn, N.** A stochastic model for COVID-19 spread and the effects of Alert Level 4 in Aotearoa New Zealand. (2020). [https://doi.org/10.1101/2020.04.08.20058743](https://doi.org/10.1101/2020.04.08.20058743)

James, A., Hendy, S. C., Plank, M. J., & **Steyn, N.** Suppression and mitigation strategies for control of COVID-19 in New Zealand. (2020). [https://doi.org/10.1101/2020.03.26.20044677](https://doi.org/10.1101/2020.03.26.20044677)

# Media

**Steyn, N.**, & Plank, M. J. Why strict border control remains crucial if we want to keep the travel bubble safe. *The Conversation.* 21 April 2021. [Link](https://theconversation.com/why-strict-border-control-remains-crucial-if-we-want-to-keep-the-travel-bubble-safe-159325)

Plank, M. J., James, A., **Steyn, N.**, & Hendy, S. C. Auckland’s rapid lockdown has given New Zealand a better chance of eliminating coronavirus – again. *The Conversation.* 28 August 2020. [Link](https://theconversation.com/aucklands-rapid-lockdown-has-given-new-zealand-a-better-chance-of-eliminating-coronavirus-again-145011)

**Steyn, N.**, Plank, M. J., James, A., Binny, R. N., Lustig, A., & Hendy, S. C. A critical error in a report on lockdown timing risks undermining future decisions. *The Spinoff.* 10 August 2020. [Link](https://thespinoff.co.nz/society/10-08-2020/a-critical-error-in-a-report-on-lockdown-timing-risks-undermining-future-decisions)

Plank, M. J., James, A., Lustig, A., **Steyn, N.**, Binny, R. N., & Hendy, S. C. A new community case of COVID-19 in New Zealand is a matter of when, not if. Is the country prepared for it? *The Conversation.* 10 August 2020. [Link](https://theconversation.com/a-new-community-case-of-covid-19-in-new-zealand-is-a-matter-of-when-not-if-is-the-country-prepared-for-it-143746)

Plank, M. J., James, A., Lustig, A., **Steyn, N.**, Binny, R. N., & Hendy, S. C. How New Zealand could keep eliminating coronavirus at its border for months to come, even as the global pandemic worsens. *The Conversation.* 16 July 2020. [Link](https://theconversation.com/how-new-zealand-could-keep-eliminating-coronavirus-at-its-border-for-months-to-come-even-as-the-global-pandemic-worsens-142368)

Plank, M. J., James, A., Lustig, A., **Steyn, N.**, Binny, R. N., & Hendy, S. C. 2 new COVID-19 cases in New Zealand, but elimination of community transmission still stands. *The Conversation.* 16 June 2020. [Link](https://theconversation.com/2-new-covid-19-cases-in-new-zealand-but-elimination-of-community-transmission-still-stands-140843)

Plank, M. J., James, A., Lustig, A., **Steyn, N.**, Binny, R. N., & Hendy, S. C. New Zealand hits a 95% chance of eliminating coronavirus – but we predict new cases will emerge. *The Conversation.* 4 June 2020. [Link](https://theconversation.com/new-zealand-hits-a-95-chance-of-eliminating-coronavirus-but-we-predict-new-cases-will-emerge-139973)

### 2025-02-11 site/papers.qmd
minor updates

@@
 
-# Pre-prints
+# Preprints
 
@@
 [Link to PDF](https://github.com/nicsteyn2/SMCforRt/blob/main/workingpaper.pdf)
+
+**Steyn, N.**, Unwin, H.
+J.
+T., Ponmattam, J., et al.
+Regional and national estimates of children affected by all-cause and COVID-19-associated orphanhood and caregiver death in Brazil, by age and family circumstance.
+*medRxiv preprint*.
+[https://doi.org/10.1101/2025.01.31.25321479](https://doi.org/10.1101/2025.01.31.25321479)
 
@@
 [Link](https://theconversation.com/new-zealand-hits-a-95-chance-of-eliminating-coronavirus-but-we-predict-new-cases-will-emerge-139973)
+
+# Awards
+
+[**Prime Minister's Science Prize**](https://pmscienceprizes.org.nz). 2020.
+Awarded for a "transformative scientific discovery or achievement" with a significant impact on New Zealand. This was awarded for our work on modelling during the COVID-19 pandemic in New Zealand.

### 2025-03-11 site/papers.qmd
update paper list

@@
 
+**Steyn, N.**, Chadeau-Hyam, M., Whitaker, M., et al.
+Pandemic-risk-related behaviour change in England from June 2020 to March 2022: REACT-1 study among over 2 million people.
+*medRxiv preprint*.
+[https://doi.org/10.1101/2025.03.03.25323250](https://doi.org/10.1101/2025.03.03.25323250)
+
 # Online resources
@@
 Provides Julia implementation of EpiEstim and EpiFilter, as well as the corresponding parameter fitting methodology developed in the paper.
+
+[Pandemic-risk-related behavioural data portal](https://m-whit-ic.shinyapps.io/react-social-shiny/): an R shiny server hosting a large quantity of aggregated data on pandemic-risk-related behaviours in England, collected as part of the REACT-1 study.
+By making these data publicly available, we hope to enable further research.
+Methodology can be found in our [preprint](https://doi.org/10.1101/2025.03.03.25323250).
 

### 2025-03-25 site/index.qmd
update with new smc preprint

@@
 
-My thesis focusses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators).
+My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators).
 My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as survey data and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).
 
-During my studies, I have also worked as a research assistant in the [*The Global Reference Group for Children Affected by Crisis*](https://www.spi.ox.ac.uk/the-global-reference-group-on-children-affected-by-covid-19#collapse3701021), estimating orphanhood in Brazil during the COVID-19 pandemic (publication coming soon), and have held a variety of tutoring positions (departmental, college, and inter-departmental courses).
+During my studies, I have also worked as a research assistant in the [*The Global Reference Group for Children Affected by Crisis*](https://www.spi.ox.ac.uk/the-global-reference-group-on-children-affected-by-covid-19#collapse3701021), estimating [orphanhood in Brazil](https://doi.org/10.1101/2025.01.31.25321479) during the COVID-19 pandemic, and have held a variety of tutoring positions (departmental, college, and inter-departmental courses).
 

### 2025-03-25 site/papers.qmd
update with new smc preprint

@@
 V.
+(2025).
 Robust uncertainty quantification in popular estimators of the instantaneous reproduction number.
@@
 **Steyn, N.**,  Parag, K.
-V., & Donnelly, C.
+V., Thompson, R.
+N., & Donnelly, C.
 A.
+(2025).
 A primer on inference and prediction with epidemic renewal models using sequential Monte Carlo methods.
-[Link to PDF](https://github.com/nicsteyn2/SMCforRt/blob/main/workingpaper.pdf)
+*arXiv preprint*.
+[https://doi.org/10.48550/arXiv.2503.18875](https://doi.org/10.48550/arXiv.2503.18875)
 
@@
 T., Ponmattam, J., et al.
+(2025).
 Regional and national estimates of children affected by all-cause and COVID-19-associated orphanhood and caregiver death in Brazil, by age and family circumstance.
@@
 **Steyn, N.**, Chadeau-Hyam, M., Whitaker, M., et al.
+(2025).
 Pandemic-risk-related behaviour change in England from June 2020 to March 2022: REACT-1 study among over 2 million people.
@@
 A., & **Steyn, N**.
+(2024).
 Jointly estimating epidemiological dynamics of Covid-19 from case and wastewater data in Aotearoa New Zealand.
@@
 J.
+(2023).
 Sensitivity of Reverse Transcription Polymerase Chain Reaction Tests for Severe Acute Respiratory Syndrome Coronavirus 2 Through Time.
@@
 A., Riley, S., & Chadeau-Hyam, M.
+(2023).
 Design and Implementation of a National SARS-CoV-2 Monitoring Program in England: REACT-1 Study.
@@
 A., & Chadeau-Hyam, M.
+(2022).
 Twin peaks: the Omicron SARS-CoV-2 BA.
@@
 C.
+(2022).
 Potential reduction in transmission of COVID-19 by digital contact tracing systems: a modelling study.
@@
 J.
+(2022).
 Effect of vaccination, border testing, and quarantine requirements on the risk of COVID-19 in New Zealand: A modelling study.
@@
 C., Lustig, A., & Ridings, K.
+(2022).
 A COVID-19 vaccination model for Aotearoa New Zealand.
@@
 N., & Lustig, A.
+(2021).
 Mathematical modelling to inform New Zealand’s COVID-19 response.
@@
 J., Hendy, S., Binny, R., Lustig, A., **Steyn, N.**, Nesdale, A., & Verrall, A.
+(2021).
 Successful contact tracing systems for COVID-19 rely on effective quarantine and isolation.
@@
 J., & Sporle, A.
+(2021).
 Māori and Pacific People in New Zealand have higher risk of hospitalisation for COVID-19.
@@
 N., Lustig, A., Hannah, K., Hendy, S.
-C., & **Steyn, N.** A structured model for COVID-19 spread: modelling age and healthcare inequities.
+C., & **Steyn, N.** (2021).
+A structured model for COVID-19 spread: modelling age and healthcare inequities.
 *Mathematical Medicine and Biology*.
@@
 J., Ridings, K.
-M., & **Steyn, N.** Early intervention is the key to success in COVID-19 control.
+M., & **Steyn, N.** (2021).
+Early intervention is the key to success in COVID-19 control.
 *Royal Society Open Science*.
@@
 C., & Lustig, A.
+(2021).
 Managing the risk of a COVID-19 outbreak from border arrivals.
@@
 
-Plank, M., James, A., & **Steyn, N.** Comment: weekly COVID-19 testing with household quarantine and contact tracing is feasible and would probably end the epidemic[^1].
+Plank, M., James, A., & **Steyn, N.** (2021).
+Comment: weekly COVID-19 testing with household quarantine and contact tracing is feasible and would probably end the epidemic[^1].
 *Royal Society Open Science*.
@@
 J., Hendy, S., Binny, R.
-N., Lustig, A., & **Steyn, N.** Model-free estimation of COVID-19 transmission dynamics from a complete outbreak.
+N., Lustig, A., & **Steyn, N.** (2021).
+Model-free estimation of COVID-19 transmission dynamics from a complete outbreak.
 *PLOS ONE*.
@@
 J., Ridings, K., & Sporle, A.
+(2020).
 Estimated inequities in COVID-19 infection fatality rates by ethnicity for Aotearoa New Zealand.
@@
 C.
+(2021).
 Modelling to support a future COVID-19 strategy for Aotearoa New Zealand.
-(2021).
 [Link to PDF](https://bpb-ap-se2.wpmucdn.com/blogs.auckland.ac.nz/dist/d/75/files/2017/01/modelling-to-support-a-future-covid-19-strategy-for-aotearoa-new-zealand.pdf)
@@
 **Steyn, N.**, Hendy, S., Plank, M., & Binny, R.
+(2021).
 Technical report: modelling the potential spread of COVID-19 during the August 2021 outbreak.
-(2021).
 [Link to PDF](https://bpb-ap-se2.wpmucdn.com/blogs.auckland.ac.nz/dist/d/75/files/2017/01/technical-report-28-august.pdf)
@@
 J.
+(2020).
 Economic comparison of the use of Alert Levels 3 and 4 in eliminating the Auckland August outbreak: a cost-effectiveness analysis 21 October 2020.
-(2020).
 [Link to PDF](https://bpb-ap-se2.wpmucdn.com/blogs.auckland.ac.nz/dist/d/75/files/2020/11/Economic-comparison-Auckland-August-outbreak_forTPMwebpage_21Oct.pdf)
@@
 C., James, A., Lustig, A., Plank, M.
-J., & **Steyn, N.** Probability of elimination for COVID-19 in Aotearoa New Zealand.
-(2020).
+J., & **Steyn, N.** (2020).
+Probability of elimination for COVID-19 in Aotearoa New Zealand.
 [https://doi.org/10.1101/2020.08.10.20172361](https://doi.org/10.1101/2020.08.10.20172361)
@@
 C., James, A., Parry, M., Plank, M.
-J., & **Steyn, N.** Effective reproduction number for COVID-19 in Aotearoa New Zealand.
-(2020).
+J., & **Steyn, N.** (2020).
+Effective reproduction number for COVID-19 in Aotearoa New Zealand.
 [https://doi.org/10.1101/2020.08.10.20172320](https://doi.org/10.1101/2020.08.10.20172320)
@@
 C., James, A., Lustig, A., Plank, M.
-J., & **Steyn, N.** Effect of Alert Level 4 on Reff: review of international COVID-19 cases.
-(2020).
+J., & **Steyn, N.** (2020).
+Effect of Alert Level 4 on Reff: review of international COVID-19 cases.
 [https://doi.org/10.1101/2020.04.30.20086934](https://doi.org/10.1101/2020.04.30.20086934)
@@
 N., Hendy, S.
-C., Lustig, A., James, A., & **Steyn, N.** A stochastic model for COVID-19 spread and the effects of Alert Level 4 in Aotearoa New Zealand.
-(2020).
+C., Lustig, A., James, A., & **Steyn, N.** (2020).
+A stochastic model for COVID-19 spread and the effects of Alert Level 4 in Aotearoa New Zealand.
 [https://doi.org/10.1101/2020.04.08.20058743](https://doi.org/10.1101/2020.04.08.20058743)
@@
 C., Plank, M.
-J., & **Steyn, N.** Suppression and mitigation strategies for control of COVID-19 in New Zealand.
-(2020).
+J., & **Steyn, N.** (2020).
+Suppression and mitigation strategies for control of COVID-19 in New Zealand.
 [https://doi.org/10.1101/2020.03.26.20044677](https://doi.org/10.1101/2020.03.26.20044677)

### 2025-04-02 site/papers.qmd
added temporally aggregated paper to research outputs

@@
 # Publications
+
+### 2025
+
+Ogi-Gittins, I., **Steyn, N.**, Polonsky, J., Hart, W.
+S., Keita, M., Ahuka-Mundeke, S., Hill, E.
+M., & Thompson, R.
+N.
+(2025).
+Simulation-based inference of the time-dependent reproduction number from temporally aggregated and under-reported disease incidence time series data.
+*Philosophical Transactions of the Royal Society A*.
+[http://doi.org/10.1098/rsta.2024.0412](https://royalsocietypublishing.org/doi/10.1098/rsta.2024.0412)
 

### 2025-04-18 site/index.qmd
added survey smoothing paper

@@
 My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators).
-My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as survey data and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).
+My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as [survey data](https://doi.org/10.1101/2025.04.16.25325936) ([see also]((https://doi.org/10.1101/2025.03.03.25323250))) and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).
 

### 2025-07-27 site/papers.qmd
added survey smoothing paper
added bioinference talk
updated publications

@@
 Robust uncertainty quantification in popular estimators of the instantaneous reproduction number.
-*medRxiv preprint*.
-[https://doi.org/10.1101/2024.10.22.24315918](https://doi.org/10.1101/2024.10.22.24315918)
+*Accepted at American Journal of Epidemiology*.
+Preprint accessible here: [https://doi.org/10.1101/2024.10.22.24315918](https://doi.org/10.1101/2024.10.22.24315918)
 
@@
 A primer on inference and prediction with epidemic renewal models using sequential Monte Carlo methods.
-*arXiv preprint*.
-[https://doi.org/10.48550/arXiv.2503.18875](https://doi.org/10.48550/arXiv.2503.18875)
+*Accepted at Statistics in Medicine*.
+Preprint accessible here: [https://doi.org/10.48550/arXiv.2503.18875](https://doi.org/10.48550/arXiv.2503.18875)
+
+**Steyn, N.**, Chadeau-Hyam, M., Elliott, P., & Donnelly, C.
+A.
+(2025).
+Bayesian modelling of repeated cross-sectional epidemic prevalence survey data.
+*medRxiv preprint*.
+[https://doi.org/10.1101/2025.04.16.25325936](https://doi.org/10.1101/2025.04.16.25325936)
 
@@
 
-# Posters
+# Talks and posters
 
@@
 
-::: {layout-ncol=2}
+::: {layout-ncol=3}
+
+![Presented at Bioinference 2025. Download [here](../files/bioinference.pdf). I was awarded the **best talk by an early career researcher** for this presentation.](../files/bioinference.png)
 

### 2025-08-04 site/papers.qmd
paper update

@@
 
-# Preprints
+# Recent publications
 
@@
 Robust uncertainty quantification in popular estimators of the instantaneous reproduction number.
-*Accepted at American Journal of Epidemiology*.
-Preprint accessible here: [https://doi.org/10.1101/2024.10.22.24315918](https://doi.org/10.1101/2024.10.22.24315918)
+*American Journal of Epidemiology*.
+[https://doi.org/10.1093/aje/kwaf165](https://doi.org/10.1093/aje/kwaf165)
+
+Ogi-Gittins, I., **Steyn, N.**, Polonsky, J., Hart, W.
+S., Keita, M., Ahuka-Mundeke, S., Hill, E.
+M., & Thompson, R.
+N.
+(2025).
+Simulation-based inference of the time-dependent reproduction number from temporally aggregated and under-reported disease incidence time series data.
+*Philosophical Transactions of the Royal Society A*.
+[http://doi.org/10.1098/rsta.2024.0412](https://royalsocietypublishing.org/doi/10.1098/rsta.2024.0412)
+
+*A complete list of publications can be found lower on this page.*
+
+# Preprints
 
@@
 ### 2025
+
+**Steyn, N.**, & Parag, K.
+V.
+(2025).
+Robust uncertainty quantification in popular estimators of the instantaneous reproduction number.
+*American Journal of Epidemiology*.
+[https://doi.org/10.1093/aje/kwaf165](https://doi.org/10.1093/aje/kwaf165)
 

### 2025-09-26 site/index.qmd
updated publications

--- 2025-03-25 site/index.qmd
@@
 
-My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on flexible methodology and [valid uncertainty quantification](https://github.com/nicsteyn2/RobustRtEstimators).
-My research combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/), and epidemiological modelling, with applications to standard epidemiological data, as well as survey data and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).
+My thesis focuses on robust statistical methods for analysing infectious disease dynamics with an emphasis on **uncertainty quantification**.
+Recent work has included developing a theoretical/philosophical decision-theoretic framework targeted for the practicalities of epidemiology ([see our preprint here](https://doi.org/10.48550/arXiv.2509.20013)), and extending existing popular methods in the field to improve the robustness of their UQ ([see our published paper here](https://doi.org/10.1093/aje/kwaf165)).
+
+Further research from my thesis combines Bayesian inference, [sequential Monte Carlo methods](http://nicsteyn2.github.io/SMCforRt/) ([see also](https://doi.org/10.1002/sim.70204)), and epidemiological modelling, with applications to standard epidemiological data, as well as [survey data](https://doi.org/10.1101/2025.04.16.25325936) ([see also]((https://doi.org/10.1101/2025.03.03.25323250))) and [wastewater-based surveillance](https://github.com/nicsteyn2/NZWastewaterModelling).
 

### 2025-09-26 site/papers.qmd
updated publications

@@
 
-Ogi-Gittins, I., **Steyn, N.**, Polonsky, J., Hart, W.
-S., Keita, M., Ahuka-Mundeke, S., Hill, E.
-M., & Thompson, R.
-N.
-(2025).
-Simulation-based inference of the time-dependent reproduction number from temporally aggregated and under-reported disease incidence time series data.
-*Philosophical Transactions of the Royal Society A*.
-[http://doi.org/10.1098/rsta.2024.0412](https://royalsocietypublishing.org/doi/10.1098/rsta.2024.0412)
-
-*A complete list of publications can be found lower on this page.*
-
-# Preprints
-
 **Steyn, N.**,  Parag, K.
@@
 (2025).
-A primer on inference and prediction with epidemic renewal models using sequential Monte Carlo methods.
-*Accepted at Statistics in Medicine*.
-Preprint accessible here: [https://doi.org/10.48550/arXiv.2503.18875](https://doi.org/10.48550/arXiv.2503.18875)
+A primer on inference and prediction with epidemic renewal models and sequential Monte Carlo.
+*Statistics in Medicine*.
+[https://doi.org/10.1002/sim.70204](https://doi.org/10.1002/sim.70204)
 
@@
 Bayesian modelling of repeated cross-sectional epidemic prevalence survey data.
-*medRxiv preprint*.
-[https://doi.org/10.1101/2025.04.16.25325936](https://doi.org/10.1101/2025.04.16.25325936)
+*Accepted in PLOS Computational Biology*.
+Preprint available here: [https://doi.org/10.1101/2025.04.16.25325936](https://doi.org/10.1101/2025.04.16.25325936)
 
@@
 Regional and national estimates of children affected by all-cause and COVID-19-associated orphanhood and caregiver death in Brazil, by age and family circumstance.
-*medRxiv preprint*.
-[https://doi.org/10.1101/2025.01.31.25321479](https://doi.org/10.1101/2025.01.31.25321479)
+*Accepted in The Lancet Regional Health Americas*.
+Preprint available here: [https://doi.org/10.1101/2025.01.31.25321479](https://doi.org/10.1101/2025.01.31.25321479)
+
+*A complete list of publications can be found lower on this page.*
+
+# Preprints
+
+**Steyn, N.**, Bickford Smith, F., Mills, C., et al.
+(2025).
+A decision-theoretic framework for uncertainty quantification in epidemiological modelling.
+*arXiv preprint*.
+[https://doi.org/10.48550/arXiv.2509.20013](https://doi.org/10.48550/arXiv.2509.20013)
 
